\textit{A young boy with a tree made of trees}: \\ Domain Adaptation of an LSTM-based Image Caption Generation Model

### 2023-01-05 paper/paper.tex
imageCLEF, some results

\pdfoutput=1
\documentclass[11pt]{article}
\usepackage{acl}
% Standard package includes
\usepackage{times}
\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}

@@

\subsection{The image captioning model \textbf{DK}}
\subsection{The code \textbf{MS and DK}}
\subsection{Flickr8k \textbf{MS or DK}}
\subsection{imageCLEF \textbf{MS or DK}}
\subsection{Human judgement questionnaire \textbf{MS}}

@@

The questionnaire itself consisted of five sections. In the first one, a modicum of personal information, such as age, gender, education, native language was collected. The following three sections were constructed the same way, and each of them corresponded to a different test set. In each of those sections, 20 images, along with the corresponding captions were presented. The order of the captions for each image was randomized to avoid bias. The participants were instructed to select one caption for each image which they thought was the best fit or the best description of the image. At the end of every section the participants had an opportunity to voice their general thoughts on the captions. Finally, in the last section the participants had the chance to include their final thoughts and opinions before submitting their answers.

@@

@@

Here we should link our repository and also make sure that it is well-organized and has proper READMEs.

>>>>

\pdfoutput=1
\documentclass[11pt]{article}
\usepackage{acl}
% Standard package includes
\usepackage{times}
\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{float}

@@

\subsection{The image captioning model \textbf{DK}}
\subsection{The code \textbf{MS and DK}}

\textit{Write about the division into files, a bit what's what, what we added and what was there. I did the evaluation part. I doubt we need to describe it in much detail, can always say that the readme has instructions and all the elements are documented, but I'd still have a bit of a summary of what we did here.}

The testing and evaluation part was conducted in a variety of Jupyter Notebook files. While the initial plan was to contain all the information in one file; unfortunately, due to GitHub limitations, that Notebook would have been too large to upload due to the number of generated ans printed image and caption pairs. Therefore, all training data sized but 2k and 5k were tested in separate notebooks using the same methods, adapted from \cite{ilinykh}, stored in a separate file, and imported into the notebook. The captions were generated using beam search and then presented together with the mappings of the attention on the image. \footnote{MS}

Other than relatively minor fixes that were required to make the code run, we decided to manually exclude the UNK token from the generation process by enforcing the lowest possible probability on it in the beam search. While this meant that we could not evaluate to what extent the models favored generating that token, it did allow us to obtain captions that sounded more natural, which was paramount for the subsequent human evaluation.\footnote{MS}

\subsection{Flickr8k \textbf{DK}}
\subsection{imageCLEF \textbf{MS}}

The second dataset used in the project was the IAPR TC-12 Benchmark, called imageCLEF in this paper. This dataset consists of 20,000 images from a variety of real life situations. Each image is paired with a description consisting of a number of consecutive utterances specifying what the image is depicting \cite{imageclef}. The assumption made in this project is that the first fragment of the description contains the most salient elements. Unlike Flickr8k, imageCLEF contains many more images that do not include people or animals. Additionally, the way the descriptions are formulated is also different from Flickr8k.

\subsection{Human judgement questionnaire \textbf{MS}}

@@

The questionnaire itself consisted of five sections. In the first one, a modicum of personal information, such as age, gender, education, native language was collected. The following three sections were constructed the same way, and each of them corresponded to a different test set. In each of those sections, 20 images, along with the corresponding captions were presented. The order of the captions for each image was randomized to avoid bias. The participants were instructed to select one caption for each image which they thought was the best fit or the best description of the image. At the end of every section the participants had an opportunity to voice their general thoughts on the captions. Finally, in the last section the participants had the chance to include their final thoughts and opinions before submitting their answers. What is important to mention is that sometimes the model could not generate a caption for a given image, or the captions were the same across multiple models. Luckily, there were always at least two different captions. Nevertheless, this does make the interpretation of the results somewhat more difficult.

@@

As described previously in the Materials and Methods section, the only models that consistently produced captions for almost all test images were the original and the "100" models. The "200" models still generated most of the captions, but many of them started being rather nonsensical or non-grammatical. This process continued in the "500" and "1000" models with fewer and fewer captions being generated successfully, and those generated ones being absolutely nonsensical. Finally in the "2k" and "5k" models most captions could not be generated.\footnote{MS} \textit{This part can be moved somewhere else if it fits better for your hyperparameters section.}

The questionnaire was filled out by 6 people. While we would like a larger sample size, we believe that we can still draw some preliminary conclusions from their answers, and that it is sufficient taking the scope of the project into account. It is also likely that the length of the questionnaire could have put off other potential respondents. The people who filled the questionnaire out ranged between 25 and 31 years of age. Three of them identified as female, two as male, one selected "other" as a response in that option. Half of the respondents had an MA/MSc degree or equivalent, two a BA/BSc or equivalent, and one selected secondary school education as the highest completed level of education. None of the people who filled the questionnaire out were native speakers of English. More detailed data about their native language was not collected.

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{1cm}|p{4.5cm}|}
\hline \bf Image & \bf Best model (\% responses) \\ \hline
15551 & 100\_0.1 (50\%)  \\
20144 & original (50\%)  \\
20343 & 100\_0.1 (33.3\%) or 100\_1.0 (33.3\%)  \\
12761 & original (33.3\%) or 100\_1.0 (33.3\%)  \\
22381 & 100\_0.1 (83.3\%) \\
10821 & 100\_0.1 (100\%) \\
18448 & original (100\%) \\
17173 & original (66.7\%) \\
13152 & original (66.7\%)  \\
20272 & original (100\%)  \\
11310 & 100\_0.1 (66.7\%)  \\
14183 & 100\_1.0 (50\%)  \\
10622 & original (50\%)  \\
13123 & original (100\%)   \\
19181 & 100\_1.0 (83.3\%) \\
16920 & 100\_0.1 (100\%) \\
11308 & original (50\%) \\
14016 & original (83.3\%) \\
21029 & original (100\%) \\
18355 & original (33.3\%) or 100\_0.15 (33.3\%) or 100\_0.2 (33.3\%) \\
\hline
\end{tabular}
\end{center}
\caption{\label{unfiltered-table} Best captions per image in the unfiltered imageCLEF test set. }
\end{table}

@@

\textit{Here we should link our repository and also make sure that it is well-organized and has proper READMEs.}
